\documentclass{resume}
\name{Miguel Ramirez}
\address{miguel.ramirez05@utrgv.edu, (956-849-6347)}
\address{Edinburg, TX} 
\begin{document}

\begin{rSection}{Education}
    {\bf University of Texas Rio Grande Valley} \hfill {2018 - 2022} 
    \\ Bachelor of Science, Computer Science.
    \\ Classification: Senior  
\end{rSection}

\begin{rSection}{Experience}
    \begin{rSubsection}{University of Texas Rio Grande Valley}{2019 - Current}{Marketing Coordinator - Office of Engaged Scholarship and Learning}{}
        \item Assisted with the creation and distribution of images and video through various channels including social and traditional media with an emphasis on establishing a consistent upload schedule.
        \item Updated and improved official webpages through front-end and back-end maintenance.
        \item Filmed and edited videos in order to explain existing programs and introduce new initiatives.
        \item Supervised the printing, laminating and exhibition of posters to promote events and workshops.
    \end{rSubsection}
    %\begin{rSubsection}{University of Texas Rio Grande Valley}{2019}{Program Mentor - UPREP Summer Program}{}
    %    \item One
    %    \item Two
    %    \item Three
    %    \item Four
    %\end{rSubsection}
\end{rSection}

\begin{rSection}{Organizations}
    \begin{rSubsection}{UTRGV Eta Omicron Nu Honor Society}{2018 - Current}{President}{}
        \item Developed programs and activities for the organization using a long-term growth mindset to ensure club longevity. 
        \item Hosted Trivia Night activities using an innovative Excel and Powerpoint approach.
        \item Assisted in the creation of images and video with the purpose of marketing the organization's events.
    \end{rSubsection}
    \begin{rSubsection}{Frontera Devs}{2020 - Current}{Marketing Lead, Co-Founder}{}
        \item Created multimedia content through an extensive research, planning, filming and editing process.
        \item Took charge in the creation and distribution of laminated posters for physical marketing purposes.
        \item Analyzed club membership statistics in order to optimize event attendance and improve marketing goals.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Competitions}
    \begin{rSubsection}{CAHSI South Texas Hackathon}{April, 2021}{General Participant}{}
        \item Participated in Cyber-Security exercises in a controlled competitive environment.
        \item Completed Digital Forensics, Cryptography and De-anonymization activities.
        \item Used a modified Kali Linux virtual machine to complete various challenges.
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages \ & C++, Java, Python and AutoHotKey.\\
    Multimedia Software \ & Adobe Creative Suite (Photoshop, After Effects, Etc.)\\
    Documents and Data \ & Microsoft Office Suite (Excel, Powerpoint, etc), LaTeX Markup.\\
    Web Development \ & Javascript, Node JS and React.\\
    Language \ & Fluent in English and Spanish.\\
    \end{tabular}
    \end{rSection}

\end{document}